### 2014-04-01 paper/discussion.tex
shortening
moar related work

\emph{Haptic} outputs are possible through compressible and incompressible fluids.  Fluids can actuate particulates and create programmable pliability \cite{Follmer-jamming}.  Additionally, use of semi-closed pipes with rubberlike material as the caps allows for gases to actuate surface features, like the back of our breathing rabbit (see Figure \ref{fig:breathe}).  Free-air haptic feedback as in Aireal \cite{Sodhi-aireal} and volumetric interactions as in Volflex \cite{Iwata-volflex} can also be pipe-mediated.

@@

\emph{Touch} sensing can be enabled through pipes filled with conductive media.  Traditional wires (threadable) may be used, but conductive paint (liquid) may be more flexible.  Using conductive paint and Swept Frequency Capacitive Sensing (SFCS \cite{Sato-touche}), an interior star pipe topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface, like our toys (see Figure \cite{fig:toys}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.

>>>>

\emph{Haptic} outputs are possible through compressible and incompressible fluids.  Fluids in pipes capped with flexible membranes can actuate particulates and create programmable pliability as in Jamming User Interfaces \cite{Follmer-jamming}.  Additionally, use of semi-closed pipes with rubberlike material as the caps allows for gases to actuate surface features, like the back of our breathing rabbit (see Figure \ref{fig:breathe}).  Free-air haptic feedback as in Aireal \cite{Sodhi-aireal} and volumetric interactions as in Volflex \cite{Iwata-volflex} can also be pipe-mediated.

@@

\emph{Touch} sensing can be enabled through pipes filled with conductive media.  Traditional wires (threadable) may be used, but conductive paint (liquid) may be more flexible.  Using conductive paint and Swept Frequency Capacitive Sensing (SFCS \cite{Sato-touche}), an interior star pipe topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface, like our toys (see Figure \cite{fig:toys}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.  Using a technique like Fiberio \cite{Holz-fiberio}, users could even be identified on touches.
